### 2018-01-23 lenses/paper.tex
added uncertainty to tables

\input{header}
\physics
\begin{document}
\papertitle{Thick Lenses}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{January 22, 2018}
\begin{paperabs}

@@

	The purpose of this experiment was to determine the index of refraction, \( n \), of a sphere and two hemispheres of different sizes made of a clear plastic. In general, refraction of light at a single spherical surface obeys the following relationship.
	\papereq{SphericalSurfaceRefraction}{\frac{n}{s} + \frac{n'}{s'} = \frac{n' - n}{R}}{Serbanescu}
	\begin{paperwhere}
		\papervar{n}{index of refraction of the first medium}{}
		\papervar{n}{index of refraction of the second medium}{}
		\papervar{s}{object distance}{\meter}
		\papervar{s'}{image distance}{\meter}
		\papervar{R}{radius of curvature}{\meter}
	\end{paperwhere}

	Applying \eqSphericalSurfaceRefraction to two spherical surfaces sharing a common axis, the Lens Maker's Formula is obtained. 
	\papereq{LensMakersFormula}{\frac{1}{f} = \pars{n-1}\pars{\frac{1}{R_1} - \frac{1}{R_2} + \frac{\pars{n-1}t}{nR_1R_2}}}{Serbanescu}
	\begin{paperwhere}
		\papervar{f}{focal length of lens}{\meter}
		\papervar{n}{index of refraction of lens}{}
		\papervar{R_1}{radius of curvature of surface closest to object}{\meter}
		\papervar{R_2}{radius of curvature of surface closest to image}{\meter}
		\papervar{t}{axial thickness of lens}{\meter}
	\end{paperwhere}

@@

	\paperfig{SmallHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{7.92}\\\paperiline
			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{7.68}\\\paperoline
		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the source.}

	\paperfig{SmallHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{6.48}\\\paperiline
			\papertableindex\papertablecval{36.10}\papertablecval{29.60}\papertablecval{6.32}\\\paperoline
		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the screen.}

		\paperfig{LargeHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
				\papertableindex\papertablecval{41.10}\papertablecval{31.00}\papertablecval{9.92}\\\paperiline
				\papertableindex\papertablecval{41.75}\papertablecval{31.35}\papertablecval{10.22}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the source.}

		\paperfig{LargeHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
				\papertableindex\papertablecval{41.85}\papertablecval{32.95}\papertablecval{8.72}\\\paperiline
				\papertableindex\papertablecval{42.40}\papertablecval{33.15}\papertablecval{9.08}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the screen.}

		\paperfig{SphereData}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
				\papertableindex\papertablecval{35.40}\papertablecval{30.40}\papertablecval{4.82}\\\paperiline
				\papertableindex\papertablecval{35.85}\papertablecval{30.50}\papertablecval{5.18}\\\paperiline
				\papertableindex\papertablecval{35.95}\papertablecval{30.55}\papertablecval{5.22}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the sphere.}

>>>>

\input{header}
\physics
\begin{document}
\papertitle{Analysis of Refractive Indices of Thick Lenses}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{January 22, 2018}
\begin{paperabs}

@@

	The purpose of this experiment was to determine the index of refraction, \( n \), of a sphere and two hemispheres of different sizes made of a clear plastic. In general, refraction of light at a single spherical surface obeys the following relationship.
	\papereq{SphericalSurfaceRefraction}{\frac{n}{s} + \frac{n'}{s'} = \frac{n' - n}{R}}{Serbanescu}
	\begin{paperwhere}
		\papervar{n}{index of refraction of the first medium}{}
		\papervar{n'}{index of refraction of the second medium}{}
		\papervar{s}{object distance}{\meter}
		\papervar{s'}{image distance}{\meter}
		\papervar{R}{radius of curvature}{\meter}
	\end{paperwhere}

	Applying \eqSphericalSurfaceRefraction to two spherical surfaces sharing a common axis, the Lens Maker's Formula is obtained. 
	\papereq{LensMakersFormula}{\frac{1}{f} = \pars{n-1}\pars{\frac{1}{R_1} - \frac{1}{R_2} + \frac{\pars{n-1}t}{nR_1R_2}}}{Serbanescu}
	\begin{paperwhere}
		\papervar{f}{focal length of lens}{\meter}
		\papervar{n}{index of refraction of lens}{}
		\papervar{R_1}{radius of curvature of surface near object}{\meter}
		\papervar{R_2}{radius of curvature of surface near image}{\meter}
		\papervar{t}{axial thickness of lens}{\meter}
	\end{paperwhere}

@@

	\paperfig{SmallHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{7.92}\\\paperiline
			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{7.68}\\\paperoline
		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the source.}

	\paperfig{SmallHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{6.48}\\\paperiline
			\papertableindex\papertablecval{36.10}\papertablecval{29.60}\papertablecval{6.32}\\\paperoline
		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the screen.}

		\paperfig{LargeHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
				\papertableindex\papertablecval{41.10}\papertablecval{31.00}\papertablecval{9.92}\\\paperiline
				\papertableindex\papertablecval{41.75}\papertablecval{31.35}\papertablecval{10.22}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the source.}

		\paperfig{LargeHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
				\papertableindex\papertablecval{41.85}\papertablecval{32.95}\papertablecval{8.72}\\\paperiline
				\papertableindex\papertablecval{42.40}\papertablecval{33.15}\papertablecval{9.08}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the screen.}

		\paperfig{SphereData}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
				\papertableindex\papertablecval{35.40}\papertablecval{30.40}\papertablecval{4.82}\\\paperiline
				\papertableindex\papertablecval{35.85}\papertablecval{30.50}\papertablecval{5.18}\\\paperiline
				\papertableindex\papertablecval{35.95}\papertablecval{30.55}\papertablecval{5.22}\\\paperoline
			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the sphere.}
